---
title: "Weight of Fish"
author: "Deztinee Saldana"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

```{r}
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
```


### Best Models

```{r}
Perchmodel1 <- lm(Weight~ .,data=Perch)
summary.lm(Perchmodel1)
```

### Best Two regressor model

```{r}
library(leaps)
Perchmodelautomate <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Perch <- summary(Perchmodelautomate)
as.data.frame(summary.Perch$outmat)
library(car)
subsets(Perchmodelautomate,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

After running this code, I found the best single element regression model (Height), the best 2 element regression models (Height and width), and I was also able to get the best 3,4 and 5 elements regression models. Statistically, how I judged the element regression models is by checking the adjusted R square values.

## Pike

```{r}
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
```


### Best Models

```{r}
Pikemodel1 <- lm(Weight~ .,data=Pike)
summary.lm(Pikemodel1)
```

### Best Two regressor model

```{r}
library(leaps)
Pikemodelautomate <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Pike <- summary(Pikemodelautomate)
as.data.frame(summary.Pike$outmat)
library(car)
subsets(Pikemodelautomate,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

After running the code for the Pike, I was able to get the best 2 regression models were Length 1 and Length 3. However,the best regression models were Length 1,2, and 3 along with Height and Width which is the complete model. All of the models were judged based on the Adjusted R square value.

## Roach

```{r}
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
```


### Best Models

```{r}
Roachmodel1 <- lm(Weight~ .,data=Roach)
summary.lm(Roachmodel1)
```

### Best Two regressor model

```{r}
library(leaps)
Roachmodelautomate <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.Roach <- summary(Roachmodelautomate)
as.data.frame(summary.Roach$outmat)
library(car)
subsets(Roachmodelautomate,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

After running the code, I was able to get all 5 regression models. The best 2 regression models were Length 3 and Width. I judged the element regression models by checking the adjusted R square values.

## Final Summary Statements